En garde! Unguarded iteration for reversible computation in the Delay monad\thanks{Niccol\`o Veltri was supported by a research grant (13156) from VILLUM FONDEN.}

### 2019-04-30 mpc19/paper.tex
minor

Though the Kleisli category of the $\Delay$ monad on $\Set$ is well studied,
comparatively less is known about this monad on other categories. It could be
interesting to study under which conditions its iterator exist -- e.g., whether
this is still the case when $\Set$ is replaced with an arbitrary topos. Another
avenue concerns the study of \emph{time invertible} programming languages:
Though not immediately clear in the current presentation, the trace on
$\Inv\Dapprox$ is not just reversible (in the sense that it preserves partial
isomorphisms) but in fact time invertible, in the sense that the number of
computation steps needed to perform $\trace (\dagger f)$ is \emph{precisely}
the same as what is needed to perform $\trace~f$ on any input. Since the
$\Delay$ monad conveniently allows the counting of computation steps, we
conjecture that this is an ideal setting in which to study such intentional
semantics of reversible programming languages.

>>>>

Though the Kleisli category of the $\Delay$ monad on $\Set$ is well studied,
comparatively less is known about this monad on other categories. It could be
interesting to study under which conditions its iterator exist -- e.g., whether
this is still the case when $\Set$ is replaced with an arbitrary topos. Another
avenue concerns the study of \emph{time invertible} programming languages:
Though not immediately clear in the current presentation, the trace on
$\Inv\Dapprox$ is not just reversible (in the sense that it preserves partial
isomorphisms) but in fact time invertible, in the sense that the number of
computation steps needed to perform $\traceD \,(\daggerD\, f)$ is \emph{precisely}
the same as what is needed to perform $\traceD\,f$ on any input. Since the
$\Delay$ monad conveniently allows the counting of computation steps, we
conjecture that this is an ideal setting in which to study such intentional
semantics of reversible programming languages.
